---
title: "Submission1-HW4"
subtitle: "Research Methods, Spring 2024"
author: "Caroline Hansen"
format:
  pdf:
    output-file: "carolinehw4-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

https://github.com/carolinezhansen/tobacco/tree/main

```{r}
#| include: false
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```

```{r}
#| include: false
#| eval: true

load("Hwk4_workspace.Rdata")
```



# Answers for Homework 4: Submission 1
\newpage

# Problem 1 
\noindent 1. Remove all SNPs, 800-series plans, and prescription drug only plans (i.e., plans that do not offer Part C benefits). Provide a box and whisker plot showing the distribution of plan counts by county over time. Do you think that the number of plans is sufficient, too few, or too many?
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"
problem1

```

\newpage
# Problem 2
\noindent 2. Remove all SNPs, 800-series plans, and prescription drug only plans (i.e., plans that do not offer Part C benefits). Provide a box and whisker plot showing the distribution of plan counts by county over time. Do you think that the number of plans is sufficient, too few, or too many?
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"
problem2
```

\newpage
# Problem 3
\noindent 3. Plot the average benchmark payment over time from 2010 through 2015. How much has the average benchmark payment risen over the years?
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"
problem3
```



\newpage
# Problem 4
\noindent 4. Plot the average share of Medicare Advantage (relative to all Medicare eligibles) over time from 2010 through 2015. Has Medicare Advantage increased or decreased in popularity? How does this share correlate with benchmark payments?
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"
problem4
```



\newpage
# Problem 5
\noindent 5. Calculate the running variable underlying the star rating. Provide a table showing the number of plans that are rounded up into a 3-star, 3.5-star, 4-star, 4.5-star, and 5-star rating.
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"

```



\newpage
# Problem 6
\noindent 6. Using the RD estimator with a bandwidth of 0.125, provide an estimate of the effect of receiving a 3-star versus a 2.5 star rating on enrollments. Repeat the exercise to estimate the effects at 3.5 stars, and summarize your results in a table.
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"

```



\newpage
# Problem 8
\noindent 8.Examine (graphically) whether contracts appear to manipulate the running variable. In other words, look at the distribution of the running variable before and after the relevent threshold values. What do you find?
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"

```



\newpage
# Problem 9
\noindent 9. Similar to question 4, examine whether plans just above the threshold values have different characteristics than contracts just below the threshold values. Use HMO and Part D status as your plan characteristics.
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"

```



\newpage
# Problem 10
\noindent 10. Summarize your findings from 5-9. What is the effect of increasing a star rating on enrollments? Briefly explain your results.
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"

```



